---
title: "Application example 6"
author: "Ting Xu (github: tingsterx/reliability_explorer)"
date: "2022-07-08"
output: github_document
---

### Comparing data aggregration strategies: A single long scan vs multiple shorter scans

How to obtain the desired amounts of data per participant is one of the challenges in the fMRI design. The same amount of data can be collected within a single long scan or multiple shorter scans data concatenation. Our previous study has demonstrated that concatenating multiple shorter scans had a clear advantage over a single long scan when the total number of time points is equal (Cho et al., 2021). This example used the data in our previous study and evaluated the change of variation between these two aggregration strategies.

**Note**: The original HCP data is not enclosed but available via the HCP (https://db.humanconnectome.org/).

Reference: [Cho et al., 2021. Impact of concatenating fMRI data on reliability for functional connectomics. NeuroImage](https://www.sciencedirect.com/science/article/pii/S105381192031034X)

## comparing data aggregration strategy

```{r load library, include=TRUE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(rstudioapi)
library(data.table)
library(dplyr)
library(ReX)
library(ggplot2)
```

### Set path
```{r set_path}
setwd(dirname(getSourceEditorContext()$path))
source('func_plot_brain_matrix.R')
data_dir <- file.path('Application6', 'data')
out_dir <- file.path('Application6', 'results')
```

### Data 

Concatenate (two shorter scans):   2subsets_concatenate_600TR_x_2segment 

Continuous (a single long scans):  2subsets_continuous_Day1_LR_and_Day1_RL 

**Note**: The HCP data is not enclosed here but available via the HCP (https://db.humanconnectome.org/).

### calcualte reliability, individual variation 
```
data_name <- '2subsets_continuous_Day1_LR_and_Day1_RL'
fname <- paste0(data_dir, '/', data_name, '/icc_in_mat.mat')
mat <- R.matlab::readMat(fname, header=TRUE)
data <- as.matrix(mat$AllData)
subID <- as.matrix(mat$sID)
session <- rep(c(1,2), times=mat$nSubj)
cov <- as.matrix(cbind(mat$CovB, mat$CovW))
df_icc <- data.frame(lme_ICC_1wayR(data, subID, session, cov))
fout <- paste0(out_dir, '/icc_1wayR__', data_name, '.csv')
fwrite(df_icc, fout)

data_name <- '2subsets_concatenate_600TR_x_2segment'
fname <- paste0(data_dir, '/', data_name, '/icc_in_mat.mat')
mat <- R.matlab::readMat(fname, header=TRUE)
data <- as.matrix(mat$AllData)
subID <- as.matrix(mat$sID)
session <- rep(c(1,2), times=mat$nSubj)
cov <- as.matrix(cbind(mat$CovB, mat$CovW))
df_icc <- data.frame(lme_ICC_1wayR(data, subID, session, cov))
fout <- paste0(out_dir, '/icc_1wayR__', data_name, '.csv')
fwrite(df_icc, fout)
```

### load the reliability, individual variation for both strategies
```{r}
fname <- paste0(out_dir, '/icc_1wayR__2subsets_continuous_Day1_LR_and_Day1_RL.csv')
df_icc1 <- fread(fname)
df_icc1$group <- '1 single 14.4min scan'
fname <- paste0(out_dir, '/icc_1wayR__2subsets_concatenate_600TR_x_2segment.csv')
df_icc2 <- fread(fname)
df_icc2$group <- '2 7.2min scans'
df_icc <- rbind(df_icc1, df_icc2)
```

### plot the individual variation in a variation field map for both strategies
```{r}
p <- rex_plot.var.field.n(df_icc, group.name = "group", size.point = 1,
                          plot.density=TRUE, show.contour = TRUE, color.point.border = NULL)
p
fname <- paste0(out_dir, '/demo_rex_plot_var_field.n__continuous_and_concatenate.pdf')
ggsave(fname, device="pdf")
```

### comparing individual variation and calcualte the gradient flow score - concatenated vs continuous
```{r}
df_baseline <- df_icc1
df_target <- df_icc2
df_paired <- cbind(df_baseline, df_target)
# calculate the normalized changes of variation - gradient flow 
df_VarPairedComp <- icc_gradient_flow(df_target$sigma2_w, df_target$sigma2_b, df_baseline$sigma2_w, df_baseline$sigma2_b)
df_VarPairedComp$contrast <- "two short scans vs a single long scans"
rownames(df_VarPairedComp) <- df_paired$X
head(df_VarPairedComp)

fname <- paste0(out_dir, '/demo_rex_plot_change__concatenate_vs_continuous.csv')
fwrite(df_VarPairedComp, fname)
```
```{r}
fname <- paste0(out_dir, '/demo_rex_plot_change__concatenate_vs_continuous.csv')
df_VarPairedComp <- fread(fname)

p <- rex_plot.var.change(df_VarPairedComp)
p
fname <- paste0(out_dir, '/demo_rex_plot_change__concatenate_vs_continuous.pdf')
ggsave(fname, device="pdf")
p <- rex_plot.icc.gradient.norm(df_VarPairedComp)
p
fname <- paste0(out_dir, '/demo_rex_plot_normalized_change__concatenate_vs_continuous.pdf')
ggsave(fname, device="pdf")
```

### plot the normalized change of individual varation (gradient flow score) - concatenated vs continuous
```{r}
# Glasser
Yeo7Network_keys <- read.csv('Application6/HCPMMP_To_Yeo7_LR.csv')$Yeo7Network_keys

Nparcel <- 360
M <- matrix(0, Nparcel, Nparcel)
M[upper.tri(M)] <- df_VarPairedComp$delta.theta_norm
M <- M + t(M) + diag(1, Nparcel)

M <- M[order(Yeo7Network_keys), order(Yeo7Network_keys)]

cmap = ReX::rgb2hex(ReX::colormap.gradient.flow())

plot_matrix_Glasser(M, cmap)

fname <- paste0(out_dir, '/demo_rex_plot_normalized_change__concatenate_vs_continuous_Matrix.png')
ggsave(fname, device="png")

```


