---
title: "Application example 4"
author: "Ting Xu (github: tingsterx/reliability_explorer)"
date: "2022-07-08"
output: github_document
---

### Examine the reliability and individual varition of 30 min vs 10 min data 

This application example compares the reliability and individual varition across four conventional fMRI pipelines including [fMRIPrep](https://fmriprep.org/en/stable/), [ABCD](https://www.biorxiv.org/content/10.1101/2021.07.09.451638v1), [CCS](https://www.sciencedirect.com/science/article/abs/pii/S2095927316305394) and [C-PAC](https://fcp-indi.github.io/docs/latest/user/index) default. The details are described in [Li et al., 2019](https://www.biorxiv.org/content/10.1101/2021.12.01.470790v1)

Raw data: Consortium for Reliability and Reproducibility (CoRR) - [HNU dataset]( http://fcon_1000.projects.nitrc.org/indi/CoRR/html/hnu_1.html)

**Calculation using ReX**: The individual variation, ICC for each edge (i.e. connectivity), and dbICC at the parcel and whole connectivity level are calcualted using the code: icc_HNU_edgewise_ICC_*.R, icc_HNU_parcelwise_dbICC_*.R, icc_HNU_AllConn_dbICC_*.R


```{r load library, include=TRUE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(rstudioapi)
library(ReX)
library(ggplot2)
library(data.table)
library(dplyr)
library(ggseg)
library(ggsegSchaefer)
```

### Set path
```{r set_path}
setwd(dirname(getSourceEditorContext()$path))
source('func_plot_brain_matrix.R')
```


### Comparing fMRI pipelines: 30min vs 10min - parcelwise
```{r}
data_dir <- file.path('Application3-5', 'results_cpac_HNU', 'ROI_Schaefer200', 'rex_dbICC_per_parcel')
out_dir <- file.path('Application3-5', 'results_cpac_HNU', 'ROI_Schaefer200', 'rex_dbICC_per_parcel_plot')

cmap = ReX::rgb2hex(ReX::colormap.gradient.flow())
atlas <- schaefer7_200$data
labels <- read.table(file.path('Application3-5', 'atlas', 'Schaefer2018_200Parcels_7Networks_labels_MatchedTo_ggseg.txt'), header = TRUE)[,1]

pipeline_list <- c("cpac_default_all_gsr", "cpac_fmriprep_all_gsr", "cpac_ccs_all_gsr", "cpac_abcd_all_gsr", 
                   "cpac_default_all", "cpac_fmriprep_all", "cpac_ccs_all", "cpac_abcd_all")

fname <- paste0(data_dir, "/dbICC_parcelwise_compare_30min_10min.csv")
df_all <- fread(fname)

for (pipeline in pipeline_list){

  prefix <- sprintf('30min_10min_%s', pipeline)
  df <- df_all %>% filter(contrast == prefix)
  df4ggseg <-  tibble(region = labels, data=df$delta.theta_norm)
    
    p <- df4ggseg %>% 
    ggseg(mapping = aes(fill = data), atlas=schaefer7_200, position="stacked") +
      scale_fill_gradientn(colours = cmap, limits= c(0, 2*pi)) +
      guides(fill = guide_colorbar(barheight=5)) +
      labs(fill = "normalized changes") + annotate(geom="text",label=NULL)
    if (grep('_gsr', pipeline)>0){
      print(sprintf('30min_10min - GSR: %s', prefix))
    }else{
        print(sprintf('30min_10min - NoGSR: %s', prefix))
    }
    print(p)
    fname <- sprintf('%s/%s_parcelwise.png', out_dir, prefix)
    ggsave(fname, device="png")
      
}
  

```