---
title: "Application example 2"
author: "Ting Xu (github: tingsterx/reliability_explorer)"
date: "2022-07-08"
output: github_document
---

### Reliability of Self-regulation test

This application example re-analyzed the self-regulation test-retest data from the previously published study [Enkavi et al., 2019](https://www.pnas.org/doi/pdf/10.1073/pnas.1818430116)

### load library
```{r setup, include=TRUE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(rstudioapi)
library(ggplot2)
library(ReX)
library(dplyr)
```

### Set path
```{r set_path, echo=FALSE}
setwd(dirname(getSourceEditorContext()$path))
data_dir <- file.path('Application2', 'Self_Regulation_Ontology')
out_dir <- file.path('Application2', 'results')
dir.create(out_dir, showWarnings = FALSE)
```

### Load the data
Raw data: https://github.com/IanEisenberg/Self_Regulation_Ontology
```{r data}
t1_dir <- paste0(data_dir, '/Data/Complete_02-16-2019')
t2_dir <- paste0(data_dir, '/Data/Retest_02-16-2019')

# time point 1
fname <- paste0(t1_dir, '/meaningful_variables_clean.csv')
df1 <- read.csv(fname, header=TRUE)
df1 <- rename(df1, "subID"="X")
# time point 2
fname <- paste0(t2_dir, '/meaningful_variables_clean.csv')
df2 <- read.csv(fname, header=TRUE)
df2 <- rename(df2, "subID"="X")
# select subjects complete both t1 and t2
df1 <- df1 %>% filter(df1$subID %in% df2$subID)
df2 <- df2 %>% filter(df2$subID %in% df1$subID)
df1_dv <- variable.names(df1[,2:dim(df1)[2]])
df2_dv <- variable.names(df2[,2:dim(df2)[2]])
write.csv(df1_dv, paste0(out_dir, '/orig_variable_names_test.csv'))
write.csv(df2_dv, paste0(out_dir, '/orig_variable_names_retest.csv'))
```

#### reorganize the variales
- delete the non-overlapped variables
- rename the variables that are not consistent in t1 and t2

```{r rename, echo=FALSE}
df1 <- subset(df1, select=-c(kirby.hyp_discount_rate_small.logTr))
df2 <- subset(df2, select=-c(holt_laury_survey.prob_weighting.ReflogTr))

df1 <- rename(df1, 'attention_network_task.conflict_hddm_drift'='attention_network_task.conflict_hddm_drift.ReflogTr',
'attention_network_task.hddm_non_decision'='attention_network_task.hddm_non_decision.ReflogTr',
'bis11_survey.Motor'='bis11_survey.Motor.logTr',
'columbia_card_task_cold.gain_sensitivity'='columbia_card_task_cold.gain_sensitivity.logTr',
'columbia_card_task_hot.loss_sensitivity'='columbia_card_task_hot.loss_sensitivity.ReflogTr',
'directed_forgetting.proactive_interference_hddm_drift'='directed_forgetting.proactive_interference_hddm_drift.logTr',
'local_global_letter.hddm_non_decision.ReflogTr'='local_global_letter.hddm_non_decision',
'motor_selective_stop_signal.hddm_thresh'='motor_selective_stop_signal.hddm_thresh.logTr')

df2 <- rename(df2, 'attention_network_task.hddm_thresh'='attention_network_task.hddm_thresh.logTr',
'columbia_card_task_cold.loss_sensitivity'='columbia_card_task_cold.loss_sensitivity.ReflogTr',
'dietary_decision.health_sensitivity'='dietary_decision.health_sensitivity.logTr',
'dietary_decision.taste_sensitivity'='dietary_decision.taste_sensitivity.ReflogTr',
'dospert_rt_survey.ethical'='dospert_rt_survey.ethical.logTr',
'dot_pattern_expectancy.hddm_drift'='dot_pattern_expectancy.hddm_drift.logTr',
'holt_laury_survey.beta.logTr'='holt_laury_survey.beta.ReflogTr',
'selection_optimization_compensation_survey.optimization.ReflogTr'='selection_optimization_compensation_survey.optimization',
'shape_matching.hddm_thresh.logTr'='shape_matching.hddm_thresh',
'simon.hddm_non_decision'='simon.hddm_non_decision.ReflogTr',
'stim_selective_stop_signal.SSRT'='stim_selective_stop_signal.SSRT.logTr',
'stim_selective_stop_signal.hddm_non_decision.ReflogTr'='stim_selective_stop_signal.hddm_non_decision',
'stop_signal.SSRT_high.logTr'='stop_signal.SSRT_high',
'stop_signal.SSRT_low'='stop_signal.SSRT_low.logTr',
'stop_signal.hddm_non_decision.ReflogTr'='stop_signal.hddm_non_decision',
'stop_signal.proactive_SSRT_speeding'='stop_signal.proactive_SSRT_speeding.logTr',
'ten_item_personality_survey.agreeableness'='ten_item_personality_survey.agreeableness.ReflogTr',
'ten_item_personality_survey.conscientiousness.ReflogTr'='ten_item_personality_survey.conscientiousness',
'threebytwo.hddm_thresh.logTr'='threebytwo.hddm_thresh',
'writing_task.positive_probability'='writing_task.positive_probability.logTr')

write.csv(variable.names(df1), paste0(out_dir, '/renamed_variable_names_test.csv'))
write.csv(variable.names(df2), paste0(out_dir, '/renamed_variable_names_retest.csv'))
```

#### find the task and survery variables
```{r survery_variables}
fname <- paste0(t1_dir, '/taskdata_clean.csv')
df1_task <- read.csv(fname, header = TRUE)
df1_task <- rename(df1_task, "subID"="X")
df1_task <- rename(df1_task, 'attention_network_task.conflict_hddm_drift'='attention_network_task.conflict_hddm_drift.ReflogTr',
'attention_network_task.hddm_non_decision'='attention_network_task.hddm_non_decision.ReflogTr',
'columbia_card_task_cold.gain_sensitivity'='columbia_card_task_cold.gain_sensitivity.logTr',
'columbia_card_task_hot.loss_sensitivity'='columbia_card_task_hot.loss_sensitivity.ReflogTr',
'directed_forgetting.proactive_interference_hddm_drift'='directed_forgetting.proactive_interference_hddm_drift.logTr',
'local_global_letter.hddm_non_decision.ReflogTr'='local_global_letter.hddm_non_decision',
'motor_selective_stop_signal.hddm_thresh'='motor_selective_stop_signal.hddm_thresh.logTr')

# get the dependent variable labels
dv_task <- variable.names(df1_task[,2:dim(df1_task)[2]])
dv_surv <- subset(variable.names(df1), !(variable.names(df1) %in% variable.names(df1_task)))
```

#### merge t1 and t2 dataframe
```{r merge_data}
df1$session = "t1"
df2$session = "t2"
df <- rbind(df1, df2)
```


### Calculate the ICC using ReX
```{r}
data <- as.matrix(subset(df, select=-c(subID, session)))
data_scale <- data
for (i in 1:dim(data)[2]){
  data_scale[,i] <- (data[,i] - min(data[,i], na.rm = TRUE))/(max(data[,i], na.rm = TRUE) - min(data[,i], na.rm = TRUE))
}
subID <- as.matrix(df[,"subID"])
session <- as.matrix(df[,"session"])
df_icc <- data.frame(lme_ICC_2wayM(data_scale, subID, session))
for (i in 1:dim(data)[2]){
  df_icc[i,'var.data'] <- var(data_scale[,i], na.rm=TRUE)
}
df_icc[(rownames(df_icc) %in% dv_task), 'measure'] <- 'task'
df_icc[(rownames(df_icc) %in% dv_surv), 'measure'] <- 'survey'

write.csv(df_icc, paste0(out_dir, '/icc_2wayM.csv'))
```

### Plot: survey vs. task in measuring the self-regulation
```{r}
p <- rex_plot.var.field.n(df_icc, group.name = 'measure')
p
fname <- paste0(out_dir, '/rex_plot_var_field.pdf')
ggsave(fname, device="pdf")
```


